Causal Compatibility Inequalities Admitting Quantum Violations in the Triangle Structure

### 2020-06-02 CCIAQVTS/CCIAQVTS.tex
made some edits to punctuation to make arxiv more on parity with PRA

    This work is the first, therefore, to find causal compatibility inequalities for the Triangle structure that are known to be violated by quantum-accessible distributions. This accomplishment was made possible through the combination of two previous developments. First, the insight of \citet{Fritz_2012} regarding the ability to re-interpret the Bell structure as a portion of the Triangle structure. Second, the new framework for solving causal inference problems developed by~\citet{Inflation} called \term{The Inflation Technique}. Ultimately, this work serves as a validation that the Inflation Technique is efficient and sensitive enough at low orders to offer new insights into quantum nonclassicality \cite{Navascues_2017}. Moreover, these new inequalities offer an avenue for recognizing previously unknown forms of nonclassicality. The authors attempts to find such novel resources were met with only partial success, suggesting the need for both conceptual refinements and future exploration.

    The first half of the manuscript, namely \Cref{sec:causal_compatibility,sec:bell_structure,sec:triangle_structure,sec:fritz_distribution}, is entirely a review of previous works. \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used. \Cref{sec:bell_structure} offers a summary of the popular Bell structure and associated inequalities. \Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research; identifying its stark differences from the Bell structure and motivating why the Triangle structure is worth studying. \Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first conceived of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}. In the same work~\cite{Fritz_2012}, the Fritz distribution was proven to be nonclassical without the use of inequalities.

    The second half of the manuscript, namely \Cref{sec:preliminary_research,sec:found_inequalities,sec:optimizations,sec:fritz_problem_revisit}, presents the main contributions made by this research project. Specifically, in \cref{sec:found_inequalities} we improve upon the results of \citet{Fritz_2012} by offering a direct proof of the incompatibility of the Fritz distribution using inequalities generated by the Inflation Technique~\cite{Inflation}. A sample of such inequalities are presented in \cref{sec:found_inequalities}, specifically \cref{eq:ww_ineq,eq:web_inequality,eq:symmetric_web_inequality}. Aside from confirming the utility of the Inflation Technique, this paper explores the importance of having derived these inequalities. First, an inequality-based proof has the advantage of being robust to experimental noise. In \cref{sec:violations_noise} the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities. Second, we numerically optimize our derived inequalities over quantum-accessible distributions (using qubits) in an effort to find the maximum violations achievable by quantum theory. The culmination of these analyses naturally prompts a discussion, found in \Cref{sec:fritz_problem_revisit}, regarding the fundamental problem of recognizing and classifying novel nonclassicality in the Triangle structure. \Cref{sec:conclusions} concludes.

@@

    Let us now contrast the classical definition of compatibility with its quantum generalization. Quantum correlation arise from a quantumified version of the causal structure, in which latent variables are replaced with quantum systems. Concretely, a distribution is accessible with quantum resources and measurements for the quantumified Bell structure if and only if there exists a bipartite quantum state $\rho_{AB}$ of arbitrary dimension, as well as Hilbert-space-localized measurement sets $M_{A|S_A}, M_{B|S_B}$\footnote{Note that a measurement set $M_{A} = \bc{M_{A}^{1}, M_{A}^{2}, \ldots, M_{A}^{k}}$ services a shorthand notation in the following sense, $\prob[A] = \Tr\bs{\rho M_{A}} \implies \prob[A]\br{a} = \Tr\bs{\rho M_{A}^{a}}$.} with indices conditional upon the measurement settings, such that
    \begin{align}\label{eq:bellQcompat}
    \prob[AB|S_AS_B] \text{ is a quantum realization of \cref{fig:bell_structure}} \quad\iff\quad\prob[AB|S_AS_B] = \Tr\bs{\rho_{AB}M_{A|S_A}\otimes M_{B|S_B}}\,.
    \end{align}
    The nonclassicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities which constrain the correlations between binary variables $A$ and $B$ for classically compatible distributions. A notable example is the CHSH inequality (\cref{eq:CHSH_ineq_orig})~\cite{CHSH_Original}.
    \[ \ba{AB | S_{A} = 0, S_{B} = 0} + \ba{AB | S_{A} = 0, S_{B} = 1} + \ba{AB | S_{A} = 1, S_{B} = 0} - \ba{AB | S_{A} = 1, S_{B} = 1} \leq 2 \eq \label[ineq]{eq:CHSH_ineq_orig} \]
    Non-trivial Bell inequalities such as the CHSH inequality are capable of witnessing the nonclassical nature of quantum distributions; the inequalities presented in \cref{sec:found_inequalities} are also of this type. Equality constraints, as previously mentioned, never have that sort of high-resolution discernment sensitivity.

@@

    The Triangle structure serves as an excellent test case for furthering our understanding of quantum nonclassicality in network causal structures. It maintains superficial simplicity (only three observable variables) while introducing many challenging features not found in the study of the Bell structure.
    For example, the spaces of both classical and quantum distributions on the Triangle structure are non-convex \cite{Fritz_2012,Inflation}, unlike for the Bell structure. The convexity of the Bell structure's distributions is arguably responsible for the wealth of knowledge about it, including its complete characterization of classicality \cite{Brunner_2013}.
    Importantly, \citet{Fritz_2012} explicitly demonstrated the existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so its known to possess quantum nonclassicality. It seems reasonable to assume that quantum nonclassicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of nonclassicality are expected to correspond to novel information-theoretical quantum advantages. A fundamental limitation of Fritz's proof of nonclassicality, however, is that it does not involve causal compatibility inequalities, and hence does not advance our repertoire of inequality constraints for the Triangle structure.
    Some inequality constraints for the Triangle structure have been derived in previous works. For example, \citet{Steudel_2010} derived an inequality distinguishing the distributions compatible with the Triangle structure from those compatible with structures in which all the observable variables share a common latent ancestor. \citet{Henson_2014} derived a family of entropic inequalities for the Triangle structure, which was the expanded somewhat by \citet{Weilenmann_2016}. Recently, \citet{Inflation} derived a variety of new, especially sensitive, polynomial causal compatibility inequalities for the Triangle structure. In particular, the inequalities of \cite{Inflation} expose a previously unclassified (as assessed by all formerly known constraints) distribution called the $w$-distribution\footnote{Although the $w$-distribution is nonclassical, it is also non-quantum. The non-quantum nature of the $w$-distribution has been demonstrated by Miguel Navascués and Elie Wolfe in private correspondence.} as incompatible with the Triangle structures.
    Remarkably, \emph{none} of the existing causal compatibility inequalities for the Triangle structure were known to admit violation by any quantum distribution. That is to say, it was unknown if any inequality known for the Triangle structure might be useful for distinguishing quantum distributions from their classical counterparts. \Cref{sec:preliminary_research} reports our attempt to utilize these aforementioned inequalities to search for incompatible distributions that are also quantum-accessible. The subsequent failure of these approaches effectively motivates the remainder of this work.
    In summary, the Triangle structure is a desirable case study because it is known to admit nonclassical distributions using quantum resources, but yet no inequality heretofore could separate its classical distributions from its quantum distributions. This failure represents a gap in our understanding of quantum nonclassicality and prompts the discovery of \textit{new} inequalities.

@@

    Fritz's problem is concerned with how to find and recognize nonclassical quantum distributions specifically for the Triangle structure. The original proof of nonclassicality essentially recycled Bell's theorem, and was limited by the requirement of perfect correlations~\cite{Fritz_2012}. Fritz's problem, as originally stated, does not require that the \emph{type} of nonclassicality be novel to the Triangle structure; rather, only that the proof should avoid Bell's theorem. \Cref{sec:preliminary_research} delineates our initial, failed attempts at resolving Fritz's problem; \Cref{sec:found_inequalities} reports our eventual success, via the discovery of new causal compatibility inequalities.

@@

    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations (in search of violation) against the previously-published compatibility inequalities of~\citet{Inflation}, as well as against the entropic inequalities of \citet{Henson_2014}. For historical context, the entropic inequalities of \cite{Henson_2014} have already been independently investigated for quantum incompatibility by \citet{Weilenmann_2016} using a variety of computational methods. Unfortunately, these methods failed to identify quantum-accessible distributions capable of violating any of the entropic inequalities considered by \cite{Weilenmann_2016}. Additionally, the inequalities presented in~\cite{Inflation} have not been previously investigated numerically.

@@

    \subsection{The Symmetric Web Inequality}
    In \cref{sec:optimizations} we will consider numerically optimizing our inequalities over quantum strategies --- seeking violations --- towards the desired end-goal of discovering new forms of nonclassicality in the Triangle structure. Of course, if some inequality achieves its optimal quantum violation on a distribution qualitatively similar to $\prob[\fritz]$, then such an inequality is unlikely to lead us to discover nonclassicality of a type different than $\prob[\fritz]$. Indeed, we will show that the previous pair of $I\tsb{WagonWheel}$ and $I\tsb{Web}$, which were both specifically curated to demonstrate the incompatibility of $\prob[\fritz]$, apparently achieve maximum quantum violation on distributions very similar to $\prob[\fritz]$ itself.

@@

    Our best numerical optimization of $I\tsb{SymmetricWeb}$ is visualized in \cref{fig:maximum_violation_I_3}. Counter-intuitively, the distribution in \cref{fig:maximum_violation_I_3} --- which achieves a greater violation of $I\tsb{SymmetricWeb}$ than $\prob[\fritz]$ --- shares its \textit{possibilistic} structure with the Fritz distribution! Additionally, since $I\tsb{SymmetricWeb}$ is symmetric with respect to the permutation of parties, one might expect that the maximum violating distribution be symmetric as well. To the contrary, our numerical optimization failed to find \emph{any} symmetric quantum distributions capable of violating $I\tsb{SymmetricWeb}$.

@@

    The injectable sets of an inflation are of \textit{principle importance} to the Inflation Technique. Given a distribution $\prob[\nodes_{O}]$ defined over the observable nodes of $\graph$, one can compute a marginal model defined over the injectable sets $\prob^{\Inj[\graph]{\graph'}} = \bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ and their images $\prob^{\ImInj[\graph]{\graph'}} = \bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$. The contrapositive of the Inflation Lemma casts the compatibility problem for $\prob^{\ImInj[\graph]{\graph'}}$ (which exhibits equivalent compatibility as $\prob[\nodes_O]$) into a compatibility problem for $\prob^{\Inj[\graph]{\graph'}}$ of any non-trivial inequalities. If $\prob^{\Inj[\graph]{\graph'}}$ is found to be incompatible with $\graph'$, then $\prob^{\ImInj[\graph]{\graph}}$ (and also $\prob[\nodes_O]$) must be incompatible with $\graph$. Fortunately, the inflated causal structure $\graph'$ possesses its own \textit{d-separation relations} which enforces conditional independence equality constraints on $\prob^{\Inj[\graph]{\graph'}}$. A useful subset of d-separation relations are those corresponding to unconditional d-separations, known as \term{ancestrally independent} sets~\cite{Pearl_2009}. Two sets $N_1', N_2'$ are ancestrally independent ($N_1' \ancestralindep N_2'$) if they have distinct ancestry in $\graph'$.
    \[ N_1' \ancestralindep N_2' \iff \An[\graph']{N_1'} \cap \An[\graph']{N_2'}= \emptyset \eq \]
    Ancestral independence implies an unconditional probabilistic independence --- if $N_1' \ancestralindep N_2'$ then $\prob[N_1' \cup N_2'] = \prob[N_1']\prob[N_2']$. If $N_1', N_2' \in \Inj[\graph]{\graph'}$, then the associated probabilistic constraint is applicable to $\prob^{\Inj[\graph]{\graph'}}$. This notion generalizes to more than two ancestrally independent sets. A set $N' \subseteq \nodes'$ is an \term{ai-expressible set} if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$. The analogous probabilistic constraint is: $\prob[N'] = \prob[\coprod_i N'_i] = \prod_{i}\prob[N'_i]$~\cite{Pearl_2009}.\footnote{In~\cite{Inflation}, this concept is generalized into terms which can be factorized via d-separation conditions and the corresponding inflated sets are termed \textit{expressible sets}. This generalization was not required for this work in particular because the ancestral independence relations formed a generating set of d-separation conditions for all of the inflations considered in \cref{fig:inflations}.} Throughout this work, we let $\AIExpr[\graph]{\graph'}$ denote the set of all ai-expressible sets.\footnote{Analogously to a marginal scenario $\mscenario$, the ai-expressible sets $\AIExpr[\graph]{\graph'}$ form an \textit{abstract simplicial complex}. Therefore, in practice, it is completely sufficient to focus on the \textit{maximal} ai-expressible sets.} Efficient algorithms for computing the injectable and ai-expressible sets of an inflation can be found in~\cite{Inflation}. \Cref{tab:asexpr_triangle_structure_wagon_wheel,tab:asexpr_triangle_structure_web} tabulate the ai-expressible sets and the associated ancestral separations for the Wagon-Wheel and Web inflations (respectively \cref{fig:wagon_wheel_inflation,fig:the_web_inflation}).

@@

    Unlike $\prob^{\ImInj[\graph]{\graph'}}$, which is non-contextual by construction, $\prob^{\Inj[\graph]{\graph'}}$ contains overlapping marginals meaning its contextuality remains unknown and must be determined using any of the techniques discussed in~\cref{sec:marginal_satisfiability}. More importantly, the Inflation Technique introduces new constraints relating to the ai-expressible sets. In practice, the equality constraints implied by $\AIExpr[\graph]{\graph'}$ permits one to construct a marginal model defined over the ai-expressible sets $\AIExpr[\graph]{\graph'}$ resulting in greater resolution in classifying the compatibility of $\prob[\nodes_O]$. In summary, the Inflation Technique partially transforms the compatibility problem into a marginal problem, wherein one can solve the marginal problem (\cref{sec:marginal_satisfiability}) to either determine the compatibility of an observable distribution $\prob[\nodes_O]$ with $\graph$ or derive compatibility inequalities for $\graph$ --- the latter of which is discussed in \cref{sec:deriving_inequalities}.

@@

    For the Triangle structure in particular, the variable permutation group is the set of permutations on $A, B, C$: $\Phi\br{\mscenario} = \Perm{A, B, C}$. For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\AIExpr[\graph]{\graph'}}$ --- an order $48$ group with the following $4$ generators:
    \begin{equation}
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_1 \\
    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_2 \\
    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_3 \\
    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_4 \\
    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
    \end{aligned}
    \end{equation}
    % ((3, 2, 1, 0, 7, 6, 5, 4, 11, 10, 9, 8),
    %  (0, 2, 1, 3, 8, 10, 9, 11, 4, 6, 5, 7),
    %  (8, 9, 10, 11, 0, 1, 2, 3, 4, 5, 6, 7),
    %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
    Notice that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the web inflation. Moreover they stabilize the ai-expressible sets of \cref{tab:asexpr_triangle_structure_web}. Importantly,
    \[ \gp\br{\AIExpr[\graph]{\graph'}} \sim \Perm{A,B,C} \eq \]
    To see this, $\varphi_1$ and $\varphi_4$ become the identity element in $\Perm{A,B,C}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.

>>>>

    This work finds causal compatibility inequalities for the Triangle structure that are known to be violated by quantum-accessible distributions. This accomplishment was made possible through the combination of two previous developments: first, the insight of \citet{Fritz_2012} regarding the ability to re-interpret the Bell structure as a portion of the Triangle structure, and second, the framework for solving causal inference problems developed by~\citet{Inflation} called \term{The Inflation Technique}. Ultimately, this work serves as a validation that the Inflation Technique is efficient and sensitive enough at low orders to offer insights into quantum nonclassicality \cite{Navascues_2017}. Moreover, these inequalities offer an avenue for recognizing previously unknown forms of nonclassicality. The authors' attempts to find such novel resources were met with only partial success, suggesting the need for both conceptual refinements and future exploration.

    The first half of the manuscript, namely \Cref{sec:causal_compatibility,sec:bell_structure,sec:triangle_structure,sec:fritz_distribution}, is entirely a review of previous works. \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used. \Cref{sec:bell_structure} offers a summary of the popular Bell structure and associated inequalities. \Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research, identifying its stark differences from the Bell structure and motivating why the Triangle structure is worth studying. \Cref{sec:fritz_distribution} defines and discusses a singularly quantum correlation first conceived of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}. In the same work~\cite{Fritz_2012}, the Fritz distribution was proven to be nonclassical without the use of inequalities.

    The second half of the manuscript, namely \Cref{sec:preliminary_research,sec:found_inequalities,sec:optimizations,sec:fritz_problem_revisit}, presents the main contributions made by this research project. Specifically, in \cref{sec:found_inequalities} we improve upon the results of \citet{Fritz_2012} by offering a direct proof of the incompatibility of the Fritz distribution using inequalities generated by the Inflation Technique~\cite{Inflation}. A sample of such inequalities is presented in \cref{sec:found_inequalities}, specifically \cref{eq:ww_ineq}, \cref{eq:web_inequality}, and \cref{eq:symmetric_web_inequality}. Aside from confirming the utility of the Inflation Technique, this paper explores the importance of having derived these inequalities. First, an inequality-based proof has the advantage of being robust to experimental noise. In \cref{sec:violations_noise} the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities. Second, we numerically optimize our derived inequalities over quantum-accessible distributions (using qubits) in an effort to find the maximum violations achievable by quantum theory. The culmination of these analyses naturally prompts a discussion, found in \Cref{sec:fritz_problem_revisit}, regarding the fundamental problem of recognizing and classifying novel nonclassicality in the Triangle structure. \Cref{sec:conclusions} concludes.

@@

    Let us now contrast the classical definition of compatibility with its quantum generalization. Quantum correlation arise from a quantumified version of the causal structure, in which latent variables are replaced with quantum systems. Concretely, a distribution is accessible with quantum resources and measurements for the quantumified Bell structure if and only if there exists a bipartite quantum state $\rho_{AB}$ of arbitrary dimension, as well as Hilbert-space-localized measurement sets $M_{A|S_A}, M_{B|S_B}$\footnote{Note that a measurement set $M_{A} = \bc{M_{A}^{1}, M_{A}^{2}, \ldots, M_{A}^{k}}$ services a shorthand notation in the following sense, $\prob[A] = \Tr\bs{\rho M_{A}} \implies \prob[A]\br{a} = \Tr\bs{\rho M_{A}^{a}}$.} with indices conditional upon the measurement settings, such that
    \begin{align}\label{eq:bellQcompat}
    \prob[AB|S_AS_B] \text{ is a quantum realization of \cref{fig:bell_structure}} \quad\iff\quad\prob[AB|S_AS_B] = \Tr\bs{\rho_{AB}M_{A|S_A}\otimes M_{B|S_B}}\,.
    \end{align}
    The nonclassicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities which constrain the correlations between binary variables $A$ and $B$ for classically compatible distributions. A notable example is the Clauser-Horne-Shimony-Holt (CHSH) inequality~\cite{CHSH_Original}.
    \[ \ba{AB | S_{A} = 0, S_{B} = 0} + \ba{AB | S_{A} = 0, S_{B} = 1} + \ba{AB | S_{A} = 1, S_{B} = 0} - \ba{AB | S_{A} = 1, S_{B} = 1} \leq 2 \eq \label[ineq]{eq:CHSH_ineq_orig} \]
    Non-trivial Bell inequalities such as the CHSH inequality are capable of witnessing the nonclassical nature of quantum distributions; the inequalities presented in \cref{sec:found_inequalities} are also of this type. Equality constraints, as previously mentioned, never have that sort of high-resolution discernment sensitivity.

@@

    The Triangle structure serves as an excellent test case for furthering our understanding of quantum nonclassicality in network causal structures. It maintains superficial simplicity (only three observable variables) while introducing many challenging features not found in the study of the Bell structure.
    For example, the spaces of both classical and quantum distributions on the Triangle structure are non-convex \cite{Fritz_2012,Inflation}, unlike for the Bell structure. The convexity of the Bell structure's distributions is arguably responsible for the wealth of knowledge about it, including its complete characterization of classicality \cite{Brunner_2013}.
    Importantly, \citet{Fritz_2012} explicitly demonstrated the existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so it is known to possess quantum nonclassicality. It seems reasonable to assume that quantum nonclassicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of nonclassicality are expected to correspond to novel information-theoretical quantum advantages. A fundamental limitation of Fritz's proof of nonclassicality, however, is that it does not involve causal compatibility inequalities, and hence does not advance our repertoire of inequality constraints for the Triangle structure.
    Some inequality constraints for the Triangle structure have been derived in previous works. For example, \citet{Steudel_2010} derived an inequality distinguishing the distributions compatible with the Triangle structure from those compatible with structures in which all the observable variables share a common latent ancestor. \citet{Henson_2014} derived a family of entropic inequalities for the Triangle structure, which was the expanded somewhat by \citet{Weilenmann_2016}. Recently, \citet{Inflation} derived a variety of new, especially sensitive, polynomial causal compatibility inequalities for the Triangle structure. In particular, the inequalities of \cite{Inflation} expose a previously unclassified (as assessed by all formerly known constraints) distribution called the $w$-distribution\footnote{Although the $w$-distribution is nonclassical, it is also non-quantum. The non-quantum nature of the $w$-distribution has been demonstrated by Miguel Navascués and Elie Wolfe in private correspondence.} as incompatible with the Triangle structures.
    Remarkably, \emph{none} of the existing causal compatibility inequalities for the Triangle structure were known to admit violation by any quantum distribution. That is to say, it was unknown if any inequality known for the Triangle structure might be useful for distinguishing quantum distributions from their classical counterparts. \Cref{sec:preliminary_research} reports our attempt to utilize these aforementioned inequalities to search for incompatible distributions that are also quantum-accessible. The subsequent failure of these approaches effectively motivates the remainder of this work.
    In summary, the Triangle structure is a desirable case study because it is known to admit nonclassical distributions using quantum resources, but yet no inequality heretofore could separate its classical distributions from its quantum distributions. This failure represents a gap in our understanding of quantum nonclassicality and prompts the discovery of \textit{new} inequalities.

@@

    Fritz's problem is concerned with how to find and recognize nonclassical quantum distributions specifically for the Triangle structure. The original proof of nonclassicality essentially recycled Bell's theorem, and was limited by the requirement of perfect correlations~\cite{Fritz_2012}. Fritz's problem, as originally stated, does not require that the \emph{type} of nonclassicality be novel to the Triangle structure, rather, only that the proof should avoid Bell's theorem. \Cref{sec:preliminary_research} delineates our initial, failed attempts at resolving Fritz's problem; \Cref{sec:found_inequalities} reports our eventual success, via the discovery of new causal compatibility inequalities.

@@

    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations (in search of violation) against the previously published compatibility inequalities of~\citet{Inflation}, as well as against the entropic inequalities of \citet{Henson_2014}. For historical context, the entropic inequalities of \cite{Henson_2014} have already been independently investigated for quantum incompatibility by \citet{Weilenmann_2016} using a variety of computational methods. Unfortunately, these methods failed to identify quantum-accessible distributions capable of violating any of the entropic inequalities considered by \cite{Weilenmann_2016}. Additionally, the inequalities presented in~\cite{Inflation} have not been previously investigated numerically.

@@

    \subsection{The Symmetric Web Inequality}
    In \cref{sec:optimizations} we will consider numerically optimizing our inequalities over quantum strategies, seeking violations, towards the desired end-goal of discovering new forms of nonclassicality in the Triangle structure. Of course, if some inequality achieves its optimal quantum violation on a distribution qualitatively similar to $\prob[\fritz]$, then such an inequality is unlikely to lead us to discover nonclassicality of a type different than $\prob[\fritz]$. Indeed, we will show that the previous pair of $I\tsb{WagonWheel}$ and $I\tsb{Web}$, which were both specifically curated to demonstrate the incompatibility of $\prob[\fritz]$, apparently achieve maximum quantum violation on distributions very similar to $\prob[\fritz]$ itself.

@@

    Our best numerical optimization of $I\tsb{SymmetricWeb}$ is visualized in \cref{fig:maximum_violation_I_3}. Counter-intuitively, the distribution in \cref{fig:maximum_violation_I_3}, which achieves a greater violation of $I\tsb{SymmetricWeb}$ than $\prob[\fritz]$, shares its \textit{possibilistic} structure with the Fritz distribution! Additionally, since $I\tsb{SymmetricWeb}$ is symmetric with respect to the permutation of parties, one might expect that the maximum violating distribution be symmetric as well. To the contrary, our numerical optimization failed to find \emph{any} symmetric quantum distributions capable of violating $I\tsb{SymmetricWeb}$.

@@

    The injectable sets of an inflation are of \textit{principle importance} to the Inflation Technique. Given a distribution $\prob[\nodes_{O}]$ defined over the observable nodes of $\graph$, one can compute a marginal model defined over the injectable sets $\prob^{\Inj[\graph]{\graph'}} = \bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ and their images $\prob^{\ImInj[\graph]{\graph'}} = \bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$. The contrapositive of the Inflation Lemma casts the compatibility problem for $\prob^{\ImInj[\graph]{\graph'}}$ (which exhibits equivalent compatibility as $\prob[\nodes_O]$) into a compatibility problem for $\prob^{\Inj[\graph]{\graph'}}$ of any non-trivial inequalities. If $\prob^{\Inj[\graph]{\graph'}}$ is found to be incompatible with $\graph'$, then $\prob^{\ImInj[\graph]{\graph}}$ (and also $\prob[\nodes_O]$) must be incompatible with $\graph$. Fortunately, the inflated causal structure $\graph'$ possesses its own \textit{d-separation relations} which enforces conditional independence equality constraints on $\prob^{\Inj[\graph]{\graph'}}$. A useful subset of d-separation relations are those corresponding to unconditional d-separations, known as \term{ancestrally independent} sets~\cite{Pearl_2009}. Two sets $N_1', N_2'$ are ancestrally independent ($N_1' \ancestralindep N_2'$) if they have distinct ancestry in $\graph'$.
    \[ N_1' \ancestralindep N_2' \iff \An[\graph']{N_1'} \cap \An[\graph']{N_2'}= \emptyset \eq \]
    Ancestral independence implies an unconditional probabilistic independence: if $N_1' \ancestralindep N_2'$ then $\prob[N_1' \cup N_2'] = \prob[N_1']\prob[N_2']$. If $N_1', N_2' \in \Inj[\graph]{\graph'}$, then the associated probabilistic constraint is applicable to $\prob^{\Inj[\graph]{\graph'}}$. This notion generalizes to more than two ancestrally independent sets. A set $N' \subseteq \nodes'$ is an \term{ai-expressible set} if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$. The analogous probabilistic constraint is: $\prob[N'] = \prob[\coprod_i N'_i] = \prod_{i}\prob[N'_i]$~\cite{Pearl_2009}.\footnote{In~\cite{Inflation}, this concept is generalized into terms which can be factorized via d-separation conditions and the corresponding inflated sets are termed \textit{expressible sets}. This generalization was not required for this work in particular because the ancestral independence relations formed a generating set of d-separation conditions for all of the inflations considered in \cref{fig:inflations}.} Throughout this work, we let $\AIExpr[\graph]{\graph'}$ denote the set of all ai-expressible sets.\footnote{Analogously to a marginal scenario $\mscenario$, the ai-expressible sets $\AIExpr[\graph]{\graph'}$ form an \textit{abstract simplicial complex}. Therefore, in practice, it is completely sufficient to focus on the \textit{maximal} ai-expressible sets.} Efficient algorithms for computing the injectable and ai-expressible sets of an inflation can be found in~\cite{Inflation}. \Cref{tab:asexpr_triangle_structure_wagon_wheel,tab:asexpr_triangle_structure_web} tabulate the ai-expressible sets and the associated ancestral separations for the Wagon-Wheel and Web inflations (respectively \cref{fig:wagon_wheel_inflation,fig:the_web_inflation}).

@@

    Unlike $\prob^{\ImInj[\graph]{\graph'}}$, which is non-contextual by construction, $\prob^{\Inj[\graph]{\graph'}}$ contains overlapping marginals meaning its contextuality remains unknown and must be determined using any of the techniques discussed in~\cref{sec:marginal_satisfiability}. More importantly, the Inflation Technique introduces new constraints relating to the ai-expressible sets. In practice, the equality constraints implied by $\AIExpr[\graph]{\graph'}$ permits one to construct a marginal model defined over the ai-expressible sets $\AIExpr[\graph]{\graph'}$ resulting in greater resolution in classifying the compatibility of $\prob[\nodes_O]$. In summary, the Inflation Technique partially transforms the compatibility problem into a marginal problem, wherein one can solve the marginal problem (\cref{sec:marginal_satisfiability}) to either determine the compatibility of an observable distribution $\prob[\nodes_O]$ with $\graph$ or derive compatibility inequalities for $\graph$, the latter of which is discussed in \cref{sec:deriving_inequalities}.

@@

    For the Triangle structure in particular, the variable permutation group is the set of permutations on $A, B, C$: $\Phi\br{\mscenario} = \Perm{A, B, C}$. For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\AIExpr[\graph]{\graph'}}$, an order $48$ group with the following $4$ generators:
    \begin{equation}
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_1 \\
    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_2 \\
    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_3 \\
    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_4 \\
    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
    \end{aligned}
    \end{equation}
    % ((3, 2, 1, 0, 7, 6, 5, 4, 11, 10, 9, 8),
    %  (0, 2, 1, 3, 8, 10, 9, 11, 4, 6, 5, 7),
    %  (8, 9, 10, 11, 0, 1, 2, 3, 4, 5, 6, 7),
    %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
    Notice that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the web inflation. Moreover they stabilize the ai-expressible sets of \cref{tab:asexpr_triangle_structure_web}. Importantly,
    \[ \gp\br{\AIExpr[\graph]{\graph'}} \sim \Perm{A,B,C} \eq \]
    To see this, $\varphi_1$ and $\varphi_4$ become the identity element in $\Perm{A,B,C}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.
